---
title: "Parse dipeptide file output and produce Cytoscape output"
output: html_notebook
---


1) separate EC/VP and EC/HC
2) select metabolites with qvalue < 0.1 and pvalue <0.05
3 Cytoscape input :
Nodes :
Node_1  Type Group_path Group_super_path
metabolite met group_path
path path path super_path
superpath superpath no superpath

Edges :
Node_1 Node_2 Type
meta   meta   meta-meta
meta   path   path
path   superpath super_path

```{r}
library(ggplot2)
library(dplyr)
```

# 1) separate EC/VP and EC/HC
```{r}
name_ana <- "dipeptide"
anova_meta <- read.csv("/home/ujjwal/Desktop/Dipeptide/data/input_dipeptides.csv")
```

```{r}
library(tidyverse)
```

## remove commas 
```{r}
#anova_meta <-anova_meta %>% mutate_all(funs(str_replace(., ",", ".")))
#anova_meta <-anova_meta %>% mutate_all(funs(str_replace(., ",", ".")))
```

```{r}
names(anova_meta)
```

```{r}
EC_VP <-select(anova_meta, Biochemical.Name, Super.Pathway, Sub.Pathway, contains("VP"))
EC_HC <-select(anova_meta, Biochemical.Name, Super.Pathway, Sub.Pathway, contains("HC"))
```

# 2) select metabolites with qvalue < 0.1 and pvalue <0.05
```{r}
EC_VP <- EC_VP[EC_VP$p.val.EC.VP. < 0.05,]
EC_VP <- EC_VP[EC_VP$q.val.EC.VP. < 0.1,]
```

```{r}
EC_HC <- EC_HC[EC_HC$p.val.EC.HC. < 0.05,]
EC_HC <- EC_HC[EC_HC$q.val.EC.HC. < 0.1,]
```

```{r}
EC_HC$sign <- NA
EC_VP$sign <- NA
```

# attribute up or down according to logFC

```{r}
for (i in 1:nrow(EC_VP)){
  if(EC_VP[i,4] > 1){
    EC_VP[i,7] <- "pos"
  }else{
    EC_VP[i,7] <- "neg"
  }
}
```

```{r}
for (i in 1:nrow(EC_HC)){
  if(EC_HC[i,4] > 1){
    EC_HC[i,7] <- "pos"
  }else{
    EC_HC[i,7] <- "neg"
  }
}
```

```{r}
names(EC_HC)[4:6] <- c("FC", "pval", "qval")
names(EC_VP)[4:6] <- c("FC", "pval", "qval")
```

#3) Build Cytoscape input

Nodes :
Node_1  Type Group_path Group_super_path
metabolite met group_path FC pval qval sig 
path path path super_path
superpath superpath no superpath

Edges :
Node_1 Node_2 Type
meta   meta   meta-meta
meta   path   path
path   superpath super_path


## Metabolites
```{r}
name_ana <- "fec_met_EC_HC"
table_nodes <- EC_HC
```

```{r}
names(table_nodes)
```
```{r}
names(table_nodes)[1:3] <- c("Node_1", "Grp_Super_Path", "Grp_Sub_Path")
table_nodes$Type <-"met"
```

```{r}
names(table_nodes)
```
## Sub pathways
```{r}
table_nodes_path <- select(table_nodes, Grp_Sub_Path, Grp_Super_Path)
table_nodes_path <- table_nodes_path[!duplicated(table_nodes_path$Grp_Sub_Path),]
```

```{r}
table_nodes_path <- data.frame(Node_1 = table_nodes_path$Grp_Sub_Path,
                               Grp_Super_Path = table_nodes_path$Grp_Super_Path,
                               Grp_Sub_Path = table_nodes_path$Grp_Sub_Path,
                               FC = NA,
                               pval = NA,
                               qval = NA,
                               sign = NA,
                               Type = "sub_path")
```


## Super pathways
```{r}
table_nodes_super_path <- table_nodes_path$Grp_Super_Path
table_nodes_super_path <- table_nodes_super_path[!duplicated(table_nodes_super_path)]
length(table_nodes_super_path)
```

```{r}
table_nodes_super_path <- data.frame(Node_1 = table_nodes_super_path,
                               Grp_Super_Path = table_nodes_super_path,
                               Grp_Sub_Path = NA,
                               FC = NA,
                               pval = NA,
                               qval = NA,
                               sign = NA,
                               Type = "super_path")
```

```{r}
table_genes <- table_nodes
```

## bind in one table

```{r}
table_nodes <- rbind(table_nodes, table_nodes_path, table_nodes_super_path)
```

```{r}
path_nodes <- paste0("results/", name_ana,  "/", name_ana, "_table_nodes.txt")
write.table(table_nodes, file = path_nodes, sep = "\t",
            row.names = TRUE, col.names = NA)
```

# NB : merge string and table edge
/home/ujjwal/Desktop/Dipeptide/results/fec_met_EC_VP/stitch_interactions_met_fec_EC_VP.tsv
stitch <- read.delim("results/fec_met_EC_HC/stitch_interactions_metabolites_fecal:EC_HC.tsv")

```{r}
#stitch <- read.delim("results/fec_met_EC_VP/stitch_interactions_met_fec_EC_VP.tsv")
stitch <- read.delim("results/fec_met_EC_HC/stitch_interactions_metabolites_fecal:EC_HC.tsv")
```


```{r}
names(stitch)
```
Edges :
Node_1 Node_2 Type
meta   meta   meta-meta x
meta   path   path
path   superpath super_path x
```{r}
names(table_nodes_path)
table_edges_path_superpath <- select(table_nodes_path, Node_1, Grp_Super_Path)
table_edges_path_superpath$Group <- "path-super_path"
```

```{r}
library(dplyr)
string <- select(stitch, X.node1, node2, node1_string_internal_id)
names(string) <-  c("Node_1", "Node_2", "Group") 
string$Group <- "met-met"
```

```{r}
names(table_nodes)
table_edges_path_meta <- select(table_genes, Node_1, Grp_Sub_Path)
table_edges_path_meta$Group <- "met-path"
names(table_edges_path_meta)
```

```{r}
names(table_edges_path_meta)[2] <-"Node_2"
names(table_edges_path_superpath)[2]<-"Node_2"
names(string)
```

```{r}
overlap <- string[string$Node_1 %in% table_genes$Node_1,]
overlap <- overlap[overlap$Node_2 %in% table_genes$Node_1,]
```

```{r}
table_edges <- rbind(overlap, table_edges_path_meta, table_edges_path_superpath)
```

```{r}
head(table_edges)
```
```{r}
head(table_nodes)
```

# save everyone
```{r}
path_edges <- paste0("results/", name_ana, "/", name_ana, "table_edges.txt")

write.table(table_edges, file = path_edges, sep = "\t",
            row.names = TRUE, col.names = NA)
```




